Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles

### 2021-08-05 source/jeb_tex/manuscript.tex
responded to Reviewer 2 comments.
updated MS and figures and supplementary based on his elaborate comments.

\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles}

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids requires the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \citep{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\citep{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \citep{RN221} and \emph{Epilachna vingtipunctuata} \citep{RN222}, rendering it immiscible with water.

The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \citep{RN145} and they can also walk underwater. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals. We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \citep{RN87}.

@@

 %The beetle's leg was constrained similar to the method described by Bullock et al \citep{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. The front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack from its claws and tibia using a pair of tweezers without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights (range: 2 - 90 mg) to get the corresponding force (resolution = 5 \textmu N). A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to measure the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion were done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder (roughly 3 mm water level). The beetle was then partially 
submerged to allow underwater contact of the pad with the substrate (immersion time $\sim$ 15 mins). In order to achieve contact without
a trapped air bubble, the water was first degassed separately in a vacuum chamber
at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. The beetle was subsequently immersed, where, the trapped air bubble within the pad dissolves into the degassed water in less than 5 mins, as verified by the ventral view contact image. Before the experiments,
the pad was brought into contact with the clean dry surface 10 times repeatedly 
to ensure the hairs are free of any contaminating particles.

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and were averaged to avoid pseudo-replication during data analysis. Experiments were repeated with 30 distinct male beetles for all combinations of contact mode (``\emph{in air}'', ``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic), 5 beetles for each  combination. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force curve with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

\begin{figure}
\includegraphics[width=3.5in]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=5 per box). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model (see text). In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary data: Movie2), unlike the other
three contact modes (supplementary data: Movie1). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air bubble trapped within
them which might not have completely dissolved away in the water.
The presence of this air-water meniscus could thus lead to elasto-capillary bundling of the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

@@

To characterise the tarsal adhesive fluid and bubble volume, we defined two
radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$. Here, $s_{f}$ and $s_{b}$
are the radii of spheres with equivalent volumes. Fluid and bubble
radii were assumed to scale proportional to their corresponding pinned
contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/(2s_{f})$
and $\phi_{b}=D_{p}/(2s_{b})$ for the fluid and bubble
respectively, to conveniently scale their volumes relative to the
hair and pad diameters they are pinned to.

The net force for cases 1 and 2 can be calculated as:

@@

@@

First, we calculated force-distance curves for a single pinned liquid
capillary bridge. Second, the effect of substrate on the force-distance
curves of the hairy pad system was compared for each mode of contact.
Third, we looked at the effect of changing the bubble
volume, $\hat{V}_{b}$, on the net underwater adhesion.
Finally, the influence of varying the hair diameter, $D_{h}$, on adhesion
was studied for each case.

@@

\begin{table}[!t]
\processtable{Fixed parameters corresponding to the pad's geometry, 
tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
\hline
\TCH{Property} & \TCH{Value} \\
\hline
Number of hairs, $N$ & 500\\
Hair diameter, $D_{h}$ & 4 \textmu m\\
Pad diameter, $D_{p}$ & 200 \textmu m\\
Hair length, $L_{h}$ & 40 \textmu m\\
Water surface tension, $\gamma_{wa}$ & 72 mN m\textsuperscript{-1}\\
Tarsal fluid-air surface tension, $\gamma_{fw}$ & 27 mN m\textsuperscript{-1}\\
Tarsal fluid-water interfacial tension, $\gamma_{fw}$ & 55 mN m\textsuperscript{-1}\\
Tarsal fluid volume, $V_{f}$ & 4 fL\\
Bubble volume, $V_{b}$ & 1 nL\\
\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=20\lyxmathsym{\textdegree}$\\
\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=56\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=93\lyxmathsym{\textdegree}$
\end{tabular*}}{}
\end{table}

@@

Forces due to a single pinned capillary liquid bridge in contact with
a substrate were obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
We see that, generally, the shape of the liquid meniscus determines
the strength of its adhesion force. High adhesion is seen for contact
angles less than $\sim$ 70\textdegree{} due to a net negative (convex) curvature
of the meniscus, while low adhesion is seen for contact angles greater
than $\sim$ 150\textdegree{} due to its net curvature being close
to zero. The Laplace pressure contribution to the net adhesion force
dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
Interestingly, its contribution to the adhesion force is mostly non-repulsive
for contact angles greater than 90\textdegree . This is because, the
low volume of the liquid and its pinned contact line prevents the
meniscus from having a high positive (concave) curvature due to geometric constraints.
Only for a contact angle of 150\textdegree , the liquid's curvature
becomes positive, manifested in its slightly repulsive Laplace contribution.
Surface tension makes a significant contribution to the net force
only for a small range of contact angles close to 90\textdegree .
For contact angles greater than 150\textdegree , the net adhesion
force approaches zero.

@@

The force-distance curves show a general trend of repulsive forces
at small distances (Figure \ref{fig:Single-bridge}a). This is a result
of the pinned contact line on the top. A limited volume is available
for the liquid to occupy when the gap distance is small, causing the
meniscus shape to bulge outwards near the pinned contact line. This
creates a net positive curvature, resulting in a positive Laplace
pressure and thus repulsion. Without pinning, the capillary forces
would have shown high attractive forces on a hydrophilic substrate\citep{RN93}. 
It is reasonable to expect the contact line to be mechanically pinned around the rim of the discoidal-shaped hair tip.
Since the male ladybug's pads are majorly composed of discoidal hairs, we proceed with this assumption to estimate the net adhesion
force of the whole pad.
%CHECK EVERYWHERE SHOULD BE DIMENSIONAL!
\subsection{Adhesion of a hairy pad: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}

The normalised force-distance curves of a hairy pad system on a hydrophilic
and hydrophobic substrate are predicted based on the capillary bridge
model and compared for the different contact modes (Figure \ref{fig:Effect-of-substrate}).
The forces in each case are calculated from equations (\ref{eq:f_air/water})
and (\ref{eq:f_bubble}) for fixed geometric and interfacial properties
(Table \ref{tab:Model-parameters}).

On the hydrophilic substrate ($\theta_{wa}=24\lyxmathsym{\textdegree}$),
highest adhesion is seen when the hairs contact in air, while lowest
adhesion occurs underwater without a trapped bubble. The presence
of a bubble leads to intermediate force values. In contrast, on a
hydrophobic substrate ($\theta_{wa}=120\lyxmathsym{\textdegree}$),
highest adhesion is seen for the underwater case without a trapped
bubble, much larger than in air. When a bubble is present, the forces
are only slightly larger than in air.

>>>>

\title{Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles}

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces \citep{DITSCHEKURU2012379,RN123}. However, underwater adhesion mediated by secreted liquids requires the displacement of the water at the interface first and a spreading of the fluid on the substrate. One approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \citep{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\citep{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \citep{RN221} and \emph{Epilachna vingtipunctuata} \citep{RN222}, rendering it immiscible with water.

The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment. Specifically, the significance of a trapped air bubble to promote underwater adhesion was resolved. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \citep{RN145} and they can also walk underwater. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's contribution in the insect's adhesion. Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals. We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \citep{RN87}.

@@

 %The beetle's leg was constrained similar to the method described by Bullock et al \citep{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. The front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to make a good contact with the substrate thus minimising partial or bad contact of the proximal pad. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue does not contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack from its claws and tibia using a pair of tweezers without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights (range: 2 - 90 mg) to get the corresponding force (resolution = 5 \textmu N). A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element (P-629.1CD, \emph{Physik Instrumente, Germany}, resolution = 3 nm), fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step for smoothing. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to measure the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
with the surface. Next, a short pause (1 s) minimized any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion were done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder (roughly 3 mm water level). The beetle (roughly 5 mm long) was then partially 
submerged to allow underwater contact of the pad with the substrate (immersion time $\sim$ 15 mins). In order to achieve contact without
a trapped air bubble, the water was first degassed separately in a vacuum chamber
at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. The beetle was subsequently immersed, where, the trapped air bubble within the pad dissolves into the degassed water in less than 5 mins, as verified by the ventral view contact image. Before the experiments,
the pad was brought into contact with the clean dry surface 10 times repeatedly (same motion protocol as described above)
to ensure the hairs are free of any contaminating particles.

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and were averaged to avoid pseudo-replication during data analysis. Experiments were repeated with distinct male beetles for each combination of contact mode (``\emph{in air}'', ``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic), using 5 beetles for each  combination. Thus, 30 distinct beetles were used in total. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, the water's contact with the beetle shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
force data was recorded, following the exact motion protocol as a typical adhesion test, but where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force curve with substrate contact, by matching the time data, to correct for the external
surface tension effects ($\sim$ 50 \textmu N) for each individual beetle. The pull-off force was subsequently calculated
from the minima as before.

@@

\begin{figure}
\includegraphics[width=3.5in]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (cream) substrates in air and underwater
conditions (n=5 per box). The small black markers show the underlying data points. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright. Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model (see text and Table \ref{tab:Model-parameters}).}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments (excluded from above analysis) using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary data: Movie2), unlike the other
three contact modes (supplementary data: Movie1). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air bubble trapped within
them which might not have completely dissolved away in the water.
The presence of this air-water meniscus could thus lead to elasto-capillary bundling of the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

The male ladybug beetles used in our experiments are known to possess mostly discoidal hairs on their distal pad. Contact images show that these hair tips are approximately circular (eccentricity $\sim$ 0.04), which could allow mechanical pinning of the secreted fluid around its perimeter. Based on this knowledge, we modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

@@

To characterise the tarsal adhesive fluid and bubble volume, we defined two
radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$. Here, $s_{f}$ and $s_{b}$
are the radii of spheres with equivalent volumes. Fluid and bubble
radii were assumed to scale proportional to their corresponding pinned
contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/(2s_{f})$
and $\phi_{b}=D_{p}/(2s_{b})$ for the fluid and bubble
respectively, to conveniently scale their volumes relative to the
hair and pad diameters they are pinned to. Larger values of $\phi_{f}$ ($\phi_{b}$) represents a smaller volume of liquid (bubble) relative to the hair (pad) that it is pinned to.

The net force of the array, $F_{net}$, for cases 1 and 2 can be calculated as:

@@

\begin{table}[!t]
\processtable{Fixed parameters corresponding to the pad's geometry, 
tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
\hline
\TCH{Property} & \TCH{Value} \\
\hline
Number of hairs, $N$ & 500\\
Hair diameter, $D_{h}$ & 4 \textmu m\\
Pad diameter, $D_{p}$ & 200 \textmu m\\
Hair length, $L$ & 40 \textmu m\\
Water surface tension, $\gamma_{wa}$ & 72 mN m\textsuperscript{-1}\\
Tarsal fluid-air surface tension, $\gamma_{fw}$ & 27 mN m\textsuperscript{-1}\\
Tarsal fluid-water interfacial tension, $\gamma_{fw}$ & 55 mN m\textsuperscript{-1}\\
Tarsal fluid volume, $V_{f}$ & 4 fL\\
Bubble volume, $V_{b}$ & 1 nL\\
\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=20\lyxmathsym{\textdegree}$\\
\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=56\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=93\lyxmathsym{\textdegree}$
\end{tabular*}}{}
\end{table}

@@

First, we calculated force-distance curves for a single pinned liquid
capillary bridge. Second, the effect of substrate on the force-distance
curves of the hairy pad system was compared for each mode of contact. The volume of the bubble would
influence it's capillary force as well as the proportion of hairs that are inside or outside the bubble.
Thus, we also looked at the effect of changing the bubble
volume, $\hat{V}_{b}$, on the net underwater adhesion.
Additionally, the influence of varying the hair diameter, $D_{h}$, on adhesion
was studied for each case, to illustrate the ``contact splitting" effect \citep{RN24}.

@@

@@

Forces due to a single pinned capillary liquid bridge in contact with
a substrate were obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
We see that, generally, the shape of the liquid meniscus determines
the strength of its adhesion force. High adhesion (> 60 \% of maximum) is seen for contact
angles less than $\sim$ 70\textdegree{} due to a net negative (convex) curvature
of the meniscus, while low adhesion (< 10 \% of maximum) is seen for contact angles greater
than $\sim$ 150\textdegree{} due to its net curvature being close
to zero. The Laplace pressure contribution to the net adhesion force
dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
Interestingly, its contribution to the adhesion force is mostly non-repulsive
for contact angles greater than 90\textdegree . This is because, the
low volume of the liquid and its pinned contact line prevents the
meniscus from having a high positive (concave) curvature due to geometric constraints.
Only for a contact angle of 150\textdegree , the liquid's curvature
becomes positive, manifested in its slightly repulsive Laplace contribution.
Surface tension makes a significant contribution to the net force
only for a small range of contact angles close to 90\textdegree .
For contact angles greater than 150\textdegree , the net adhesion
force approaches zero.

@@

The force-distance curves show a general trend of repulsive forces
at small distances, a minima at an intermediate distance corresponding to the adhesion force, and finally tending to zero force at large distances until the capillary bridge ruptures (Figure \ref{fig:Single-bridge}a). The repulsive force seen at small distances is a result
of the pinned contact line on the top. A limited volume is available
for the liquid to occupy when the gap distance is small, causing the
meniscus shape to bulge outwards near the pinned contact line. This
creates a net positive curvature, resulting in a positive Laplace
pressure and thus repulsion. Without pinning, the capillary forces
would have shown high attractive forces on a hydrophilic substrate \citep{RN93}. 
It is reasonable to expect the contact line to be mechanically pinned around the rim of the discoidal-shaped hair tip.
Since the male ladybug's pads are majorly composed of discoidal hairs, we proceed with this assumption to estimate the net adhesion
force of the whole pad.
%CHECK EVERYWHERE SHOULD BE DIMENSIONAL!
\subsection{Adhesion of a hairy pad: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}

The force-distance curves of a hairy pad system on a hydrophilic
and hydrophobic substrate are predicted based on the capillary bridge
model and compared for the different contact modes (Figure \ref{fig:Effect-of-substrate}).
The forces in each case are calculated from equations (\ref{eq:f_air/water})
and (\ref{eq:f_bubble}) for fixed geometric and interfacial properties
(Table \ref{tab:Model-parameters}).

On the hydrophilic substrate ($\theta_{wa}=20\lyxmathsym{\textdegree}$),
highest adhesion is seen when the hairs contact in air, while lowest
adhesion occurs underwater without a trapped bubble. The presence
of a bubble leads to intermediate force values. In contrast, on a
hydrophobic substrate ($\theta_{wa}=93\lyxmathsym{\textdegree}$),
highest adhesion is seen for the underwater case without a trapped
bubble, much larger than in air. When a bubble is present, the forces
are only slightly larger than in air.

\begin{figure*}
\centering
\includegraphics[width=6in]{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
of a hairy pad on a hydrophilic and hydrophobic substrate in
air and underwater conditions. A negative force value represents attraction.
Forces are calculated from the capillary bridge model,
with model parameters listed in Table \ref{tab:Model-parameters}.
The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Insets represent the \emph{underwater:
bubble} contact for each substrate.}
\end{figure*}
